Reading Notes

### 2020-07-30 2pd.tex
added <> for ideas to get going in each section

\section*{Research Objectives}

@@

\subsection*{Organic Photovoltaics}

@@

@@

\subsection*{Multi-State Iterative Boltzmann Inversion}
<how cg potentials have been obtained>
<IBI>
<why are IBI potentials not transferrable? the RDF is a property of the ensemble average at a given statepoint so the potential derived from this property is also limited.>
separate potentials are required to capture solid and fluid structures of a pure simple lipid <Moore2014 ref 46>
<IBI potentials are sometimes transferrable and it is not clear why sometimes they are and sometimes they aren't.> \cite{Moore2014}

@@

\subsection*{Mesoscale Device Simulation}

\section*{Preliminary Work}
<Talk about what exists and why it is not enough>
<votca, Peng2019a> 
Versatile Object-oriented Toolkit for Coarse-graining Applications (VOTCA) \cite{Ruhle2011b}
includes a coarse-graining, forcefield creation with reverse MC or IBI, and back-mapping modules.
It also allows for charge transport calculations using KMC similar to MorphCT <cite>

@@

- contributed to development of open-source packages: mbuild, foyer, signac, fresnel
 this has helped me learn best software development practices like writing documentation, using version control, writing unit tests, employing CI, fork/pull model, etc.
using these tools will help me to me a more efficient developer.
It's also helped me to learn how to work as part of a team.
 - created MWE of coarse-graining and backmapping with smiles-- these will need furthertesting as we try them on different compounds but the proof of concept is there.
 - created tutorial examples to help current and future students understand scientific concepts and how to use computational tools
 - created GIXStapose (presented at SciPy2020) an interactive diffraction/structure viewer.
This may seem unrelated but we can use diffraction to verify our opv morphologies and compare them to experiment.
GIXStapose helps to beeter connect the physical structure with the diffraction pattern.
- started development on UFF repo for foyer.
This is an example of how to create a version controlled forcefield which can be automatically applied to a compound.
(atom typing is a pain)

@@

\section*{Contingency Analysis}
what's going to be hard?

>>>>

\section*{Research Objectives}
<gain insight into the limits of coarse graining>
<create models for new opv compounds>
<create a workflow that will make creating new models more accessible>
<develop new tools that help humans do science>
<I don't know where to put this but I want a section on best practices>
By making our code open source and freely availiable, we contribute to the knowledge of a global community. But just because something is availiable doesn't mean it is accessible. 
lazy refactoring--get something working first then update it when needed, keep code small and modular to make this easier and more understandable\cite{Adorf2018a} 
Best practices for jupyter notebooks -- like a lab notebook-- can show the process and the story of each assignment and the exact steps and results to get there\cite{Rule2019a}
Using software carpentry principles to keep in mind how people learn when introducing a new concept\cite{https://v4.software-carpentry.org/softeng/principles.html}
reducing cognitive load \cite{Jankowski2019}
using the tools, not fighting them--version control, automation \cite{Wilson2014}
TRUE\cite{Thompson2020}

@@

\subsection*{Organic Photovoltaics}
<history>
<how opvs work>
<why morphology matters>
<segue into simulation>

@@

<md in general>
<what assumptions does md make?>
<what are the limits of atomistic md?>

@@

<how cg potentials have been attained>
\subsection*{Multi-State Iterative Boltzmann Inversion}
<IBI>
<why are IBI potentials not transferrable? the RDF is a property of the ensemble average at a given statepoint so the potential derived from this property is also limited.>
separate potentials are required to capture solid and fluid structures of a pure simple lipid <Moore2014 ref 46>
<IBI potentials are sometimes transferrable and it is not clear why sometimes they are and sometimes they aren't.> \cite{Moore2014}

@@

\subsection*{Mesoscale Device Simulation}
<how morphct pipeline would work: cg-backmap-ct>
<how kmc works>
<cite morphct papers>

\section*{Preliminary Work}
- contributed to development of open-source packages: mbuild, foyer, signac, fresnel
 this has helped me learn best software development practices like writing documentation, using version control, writing unit tests, employing CI, fork/pull model, etc.
using these tools will help me to me a more efficient developer.
It's also helped me to learn how to work as part of a team.
 - created MWE of coarse-graining and backmapping with smiles-- these will need furthertesting as we try them on different compounds but the proof of concept is there.
 - created tutorial examples to help current and future students understand scientific concepts and how to use computational tools
 - created GIXStapose (presented at SciPy2020) an interactive diffraction/structure viewer.
This may seem unrelated but we can use diffraction to verify our opv morphologies and compare them to experiment.
GIXStapose helps to beeter connect the physical structure with the diffraction pattern.
- started development on UFF repo for foyer.
This is an example of how to create a version controlled forcefield which can be automatically applied to a compound.
<atom typing is a pain and doing it manually is bad cite foyer paper>

<Talk about what exists and why it is not enough>
<votca, Peng2019a> 
Versatile Object-oriented Toolkit for Coarse-graining Applications (VOTCA) \cite{Ruhle2011b}
includes a coarse-graining, forcefield creation with reverse MC or IBI, and back-mapping modules.
It also allows for charge transport calculations using KMC similar to MorphCT <cite>

@@

@@

\section*{Contingency Analysis}
<what's going to be hard?>
